Enforced Invariant Confluence

### 2018-02-18 doc/paper_redux/sufficient_conditions.tex
Tweak to sufficient conditions.

The conditions in \clmref{statebasedsufficient} and \clmref{opbasedsufficient}
are not necessary. Intuitively, this makes quite a bit of sense. Neither
condition depended on the initial state $s_0$, and both
\clmref{statebasednotnecessary} and \clmref{opbasednotnecessary} exploit this.
If we relax our assumption of a fixed start state, then both these conditions
become sufficient and necessary.

\todo{Prove this more carefully. It's pretty straightforward though.}

>>>>

The conditions in \clmref{statebasedsufficient} and \clmref{opbasedsufficient}
are not necessary. Intuitively, this makes quite a bit of sense. Neither
condition depends on the initial state $s_0$, and both
\clmref{statebasednotnecessary} and \clmref{opbasednotnecessary} exploit this.
If we relax our assumption of a fixed start state, then both these conditions
are sufficient and necessary. Similarly, if every state in $S$ is reachable
from $s_0$, then the conditions are sufficient and necessary.

\todo{Prove these facts more carefully. It's pretty straightforward though.}
